---
title: "Campaign"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

options(digits = 4)
library(tidyverse)
library(lubridate)
library(janitor)
library(here)


# Hex color codes for Democrat Blue and Republican Red
party_colors <- c("#2E74C0", "#CB454A")


# Make sure you use readr::read_csv() as it is significantly faster than read.csv()
CA_contributors_2016 <- read_csv(here::here("data", "CA_contributors_2016.csv"))

glimpse(CA_contributors_2016)

```{r}
# Top 10 Candidates with highest Contribution 
total_contrb<-CA_contributors_2016 %>%
  group_by(cand_nm) %>%
  summarise(Total_contb=sum(contb_receipt_amt)) %>%
  arrange(desc(Total_contb)) %>%
  mutate(highlight_clinton = ifelse(cand_nm == 'Clinton, Hillary Rodham', T, F)) %>% 
   ggplot(top_10_candidates,mapping=aes(x=Total_contb/10^6, y=reorder(cand_nm,Total_contb))) +
  geom_col(aes(fill=highlight_clinton)) +
     labs(title= "Candidates with highest contribution", 
       x= "Total Contribution in million $",
       y="")+
  theme_classic()+
  scale_fill_manual(values = c('#595959', 'blue'))+
  theme(legend.position = 'none')+
     NULL
  
total_contrb
```

# Top 10 candidates with highest average donation

```{r}
mean_contrb<-CA_contributors_2016 %>% 
  group_by(cand_nm) %>% 
  summarise(mean_contb=mean(contb_receipt_amt)) %>%
  slice_max(n=10,mean_contb)%>%
  ggplot(aes(x=mean_contb,y=reorder(cand_nm, mean_contb)))+
  geom_col()+
  labs(title = "Top 10 candidates with highest average contribution",
       x= "Average contribution ($)",
       y="")+
  theme_classic()+
  NULL

mean_contrb
```


```{r}
# What was the median contribution?
median_contrb<-CA_contributors_2016 %>% 
  group_by(cand_nm) %>% 
  summarise(median_contb=median(contb_receipt_amt)) %>%
  mutate(highlight_clinton = ifelse(cand_nm == 'Clinton, Hillary Rodham', T, F)) %>% 
    ggplot(aes(x=median_contb,y=reorder(cand_nm, median_contb)))+
  geom_col(aes(fill=highlight_clinton))+
  labs(title = "Candidates with the highest median contributions",
       x= "Median contribution ($)",
       y="")+
  theme_classic()+
    scale_fill_manual(values = c('#595959', 'blue'))+
    theme(legend.position = "none")+
           NULL

median_contrb

```

```{r}
library(patchwork)

patchwork<-total_contrb + median_contrb
patchwork +
  plot_annotation(title = 'The candidate with the highest contribution has the lowest median contribution!',
                  theme = theme(plot.title = element_text(size = 18))) 


# Challenge 2 What were the top 10 cities in terms of total_contribution for each of the two candidates 

```{r}
ZIPcodes = vroom::vroom(here::here("data","zip_code_database.csv"))
CA_contributors_join <- merge(CA_contributors_2016,ZIPcodes, by = "zip")
CA_contributors_join_cleaned <- CA_contributors_join %>%
  select(zip, cand_nm, contb_receipt_amt, primary_city)

Clinton <- CA_contributors_join_cleaned %>%
  filter(cand_nm == "Clinton, Hillary Rodham") %>%
  group_by(primary_city) %>%
  summarise(total = sum(contb_receipt_amt)) %>%
  arrange(desc(total)) %>%
  slice_max(n=5, total)

Trump <- CA_contributors_join_cleaned %>%
  filter(cand_nm == "Trump, Donald J.") %>%
  group_by(primary_city) %>%
  summarise(total = sum(contb_receipt_amt)) %>%
  arrange(desc(total)) %>%
  slice_max(n=5, total)

Clinton_plot<-ggplot(Clinton, mapping = aes(x = total, y = reorder(primary_city,total))) +
  geom_col(fill = "blue3")+
  labs(
    x = "Amount raised",
    y= "" ,
    title = "Clinton, Hillary Rodham") + 
  scale_x_continuous(labels=scales::dollar) +
  NULL

Trump_plot<-ggplot(Trump, mapping = aes(x = total, y = reorder(primary_city,total))) +
  geom_col(fill = "red3")+
  labs(
    x = "Amount raised",
    y= "" ,
    title = "Trump, Donald J.") + 
  scale_x_continuous(labels=scales::dollar) +
  NULL

patchwork_cand<-Clinton_plot+Trump_plot
patchwork_cand+plot_annotation(title="Which states contributed the most?")

```
